Computing exact restricted isometry constants via\\ mixed integer semidefinite programming

### 2015-01-02 RIP-MISDP-Paper/Paper_v1.tex
rename environment for definitions

\newtheorem{thm}{Theorem}
\newdefinition{rmk}{Definition}

@@

\begin{rmk}\label{ripdef}
  The \emph{restricted isometry property} (RIP) of order~$k$ holds for a
  matrix $A \in \R^{m \times n}$ with constant~$\delta \geq 0$, if
  \begin{equation}\label{rip}
    (1 - \delta) \Norm{x}{2}^2 \leq \Norm{Ax}{2}^2 \leq (1+\delta) \Norm{x}{2}^2
  \end{equation}
  for all $x \in \Sigma_k \define \{x \in \R^n \suchthat \Norm{x}{0} \leq k\}$. The
  smallest constant~$\delta$ such that~\eqref{rip} holds is called
  \emph{restricted isometry constant} (RIC)~$\delta_k$.
\end{rmk}

@@

\begin{rmk}\label{asymRIPdef}
 The \emph{lower} and \emph{upper RIC} are defined as
 \begin{align}
   \alpha_k & \define \argmax_{\alpha \geq 0}\; \{ \alpha^2 \Norm{x}{2}^2
   \leq \Norm{Ax}{2}^2,\; \text{ for all }x \in \Sigma_k\}\text{ and }\label{lowerRIP}\\
   \beta_k & \define \argmin_{\beta \geq 1}\; \{ \Norm{Ax}{2}^2 \leq \beta^2
   \Norm{x}{2}^2,\; \text{ for all }x \in \Sigma_k\},\label{upperRIP}
 \end{align}
 respectively. The \emph{restricted isometry ratio} (RIR) $\gamma_k$ is
 defined as $\gamma_k \define \beta_k^2 / \alpha_k^2$.
\end{rmk}

>>>>

\newtheorem{thm}{Theorem}
\newdefinition{definition}{Definition}

@@

\begin{definition}\label{ripdef}
  The \emph{restricted isometry property} (RIP) of order~$k$ holds for a
  matrix $A \in \R^{m \times n}$ with constant~$\delta \geq 0$, if
  \begin{equation}\label{rip}
    (1 - \delta) \Norm{x}{2}^2 \leq \Norm{Ax}{2}^2 \leq (1+\delta) \Norm{x}{2}^2
  \end{equation}
  for all $x \in \Sigma_k \define \{x \in \R^n \suchthat \Norm{x}{0} \leq k\}$. The
  smallest constant~$\delta$ such that~\eqref{rip} holds is called
  \emph{restricted isometry constant} (RIC)~$\delta_k$.
\end{definition}

@@

\begin{definition}\label{asymRIPdef}
 The \emph{lower} and \emph{upper RIC} are defined as
 \begin{align}
   \alpha_k & \define \argmax_{\alpha \geq 0}\; \{ \alpha^2 \Norm{x}{2}^2
   \leq \Norm{Ax}{2}^2,\; \text{ for all }x \in \Sigma_k\}\text{ and }\label{lowerRIP}\\
   \beta_k & \define \argmin_{\beta \geq 1}\; \{ \Norm{Ax}{2}^2 \leq \beta^2
   \Norm{x}{2}^2,\; \text{ for all }x \in \Sigma_k\},\label{upperRIP}
 \end{align}
 respectively. The \emph{restricted isometry ratio} (RIR) $\gamma_k$ is
 defined as $\gamma_k \define \beta_k^2 / \alpha_k^2$.
\end{definition}
